Untitled

### 2014-12-02 Misc/TrialFile.Rmd
Created a map of Opportunity data and worked on cleaning WayofTeaching data

@@

# Arrange subset_data by country and year
GrandData <- arrange(subset_data, Country, Year)

GrandData1 <- GrandData[order("Country",)]

>>>>

``` {r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE}

# Country code
rm(CleanGEM)
dfs <- ls()[1:max(grep(pattern = 'Clean[0-1]*', x = ls()))]

for (i in dfs){
  message(i)
  temp <- get(i)
  names_temp <- names(temp)
  temp[, 'year'] <- names_temp[2]
  names(temp) <- c('Country', 'WayofTeaching', 'year')

    if (i == 'Clean01') {
      cleaned <- temp
  } else if (i != 'Clean01'){
      cleaned <- rbind(cleaned, temp)
  }
}

# Country code
# Subset

@@

# Arrange subset_data by country and year
GData <- arrange(subset_data, Country, Year)

GData <- GData[order("Country",)]
